---
title: "Zebrafish Heatmaps"
author: "Daniela Moura"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r}
library(dplyr)
library(ggplot2)
library(reshape2)
```


Neuroactive Ligand Receptor Interaction
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Neuroactive-ligand-receptor-interaction.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Neuroactive Ligand Receptor Interaction (mid brain)") +
  theme_classic()
```


Cocaine Addiction
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Cocaine-addiction.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Cocaine addiction genes (mid brain)") +
  theme_classic()
```
    
      
Dopaminergic-synapse
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Dopaminergic-synapse.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Dopaminergic synapse (mid brain)") +
  theme_classic()

```

CAMP-signaling-pathway
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\CAMP-signaling-pathway.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "CAMP signaling pathway (mid brain)") +
  theme_classic()
```

Amphetamine-addiction
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Amphetamine-addiction.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Amphetamine addiction (mid brain)") +
  theme_classic()
```

     
Chemical Carcinogenesis
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Chemical-carcinogenesis.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Chemical Carcinogenesis (mid brain)") +
  theme_classic()
```

Drug Metabolism
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Drug-metabolism.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Drug Metabolism (mid brain)") +
  theme_classic()
```


Nicotine Addiction
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Nicotine-addiction.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Nicotine Addiction (mid brain)") +
  theme_classic()

```


Metabolism of Xenobiotics by Cytochrome P450
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Metabolism-of-xenobiotics-by-cytochrome-P450.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Metabolism of Xenobiotics by Cytochrome P450 (mid brain)") +
  theme_classic()
```

Alcoholism
```{r}

file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Alcoholism.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Alcoholism (mid brain)") +
  theme_classic()
```


Cholinergic Synapse
```{r}

file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Cholinergic-synapse.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Cholinergic Synapse (mid brain)") +
  theme_classic()
```

Serotonergic Synapse
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Serotonergic-synapse.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Serotonergic Synapse (mid brain)") +
  theme_classic()
```

Morphine Addiction
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Morphine-addiction.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Morphine Addiction (mid brain)") +
  theme_classic()
```



Calcium Signaling Pathway
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Calcium-signaling-pathway.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Calcium Signaling Pathway (mid brain)") +
  theme_classic()
```

Tryptophan Metabolism
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Tryptophan-metabolism.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Tryptophan Metabolism (mid brain)") +
  theme_classic()
```


Glutamatergic Synapse
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Glutamatergic-synapse.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Glutamatergic Synapse (mid brain)") +
  theme_classic()
```

Tyrosine Metabolism
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Tyrosine-metabolism.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Tyrosine Metabolism (mid brain)") +
  theme_classic()
```


Estrogen Signaling Pathway
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Estrogen-signaling-pathway.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Estrogen Signaling Pathway (mid brain)") +
  theme_classic()
```

Rap1 Signaling Pathway
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Rap1-signaling-pathway.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Rap1 Signaling Pathway (mid brain)") +
  theme_classic()
```
    
  
Steroid Hormone Biosynthesis
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Steroid-hormone-biosynthesis.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Gene"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Gene)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "Steroid Hormone Biosynthesis (mid brain)") +
  theme_classic()
```
    
chrna Family
```{r}
file <- read.csv("Astar_22July\\Files\\MidBrain\\Heatmaps\\Chrna_family.csv", header=TRUE, sep=",")

means <- file

#Including means by fish type
means <- mutate(means, wild_type = (MB_WT_1 + MB_WT_2 + MB_WT_3)/3) 
means <- mutate(means, mutant_2 = (MB_MUT2_1 + MB_MUT2_2 + MB_MUT2_3)/3) 
means <- mutate(means, mutant_4 = (MB_MUT4_1 + MB_MUT4_2 + MB_MUT4_3)/3) 

#Selecting only coluumns with means
means <- means[,c(1,11,12,13)]

#Reshaping
means <- melt(means, id = c("Genes"))
colnames(means)[2] <- "fish_type"
colnames(means)[3] <- "gene_count"

ggplot(means, aes(x = fish_type, y = Genes)) + geom_raster(aes(fill = gene_count)) +
  scale_fill_gradient(low = "white", high = "black") +
  labs(x = "fish type", y = "gene", title = "chrna family (mid brain)") +
  theme_classic()
```

